---
title: "HuntingvsLivestockFarming_20200516"
author: "CWBrink_list"
date: "16/05/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Supplementary Feeding Site Managers: Livestock farming versus hunting operations

This document shows the analysis associated with the paper titled "Perceptions of vulture supplementary feeding site managers and potential hidden risks to avian scavengers", published in Conservation Science and Practice in 2020. The analysis explores data from a questionnaire survey with vulture supplementary feeding site (SFS) managers to determine the extent of problematic management practices that may endanger vultures. It is advisable to read the results of the paper to give context to the code provided below.

The raw data associated with the analysis can unfortunately not be shared at this time.

This analysis compares vulture supplementary feeding site (SFS) managers who rely on livestock farmer as opposed to hunting opperations in terms of their overall and individual knowledge of threats to vultures and their percieved benefits and disadvantages to managing a SFs.

```{r package installation, echo= FALSE, warning=FALSE, message=FALSE, include=TRUE, results='hide'}

rm(list=ls())

library (tidyverse)
library(ggplot2)
library (dplyr)
library(tidyr)
library(DHARMa)
library(car)
library(emmeans)
library(effects)
library(MASS)
library(rcompanion)
library(readr)

getwd()
Chpt1B_Data<- read_delim("VRResponses_FINAL_Rworksheet_20191021_CheckedRefined_ActiveSiteCatAdjusted.csv", 
                         ";", escape_double = FALSE, trim_ws = TRUE)

Raw_Data <- as_tibble(Chpt1B_Data)

Data <- Raw_Data %>%
  dplyr::select(., -Number, -Date_Interviewed, -Method, -Time_Start,
               -Time_End, -Language_Survey, -Name_Respondent)%>%
  as_tibble(.)

Data <- as_tibble(Data)
options("na.action")

```

```{r Subset to only Active}
#Need to subset only active SFS in SA - questions such as best practices are only relevent to currely active SFS.

Active_SFS <- Data %>%
  filter(., Status_Category == "Active", Country == "South Africa")


Active_SFS <- Active_SFS %>% mutate(., Catagory_Activity = 
                                      ifelse(MainActiv_LivestockfarmSUM == 1 & MainActiv_Hunting == 0, "Livestock", 
                                             ifelse(MainActiv_LivestockfarmSUM == 0 & MainActiv_Hunting == 1, "Hunting", 
                                                    ifelse(MainActiv_LivestockfarmSUM == 1 & MainActiv_Hunting == 1, "Combined", "NA"))))

Comparison_L_H <- subset(Active_SFS, Catagory_Activity == "Livestock" | Catagory_Activity == "Hunting") 

Comparison_L_H$Catagory_Activity <- factor(Comparison_L_H$Catagory_Activity, levels = c("Livestock", "Hunting"))

Comparison_L_H <- Comparison_L_H %>% mutate(., Catagory_Activity_Binary =
                                              as.numeric(ifelse(Catagory_Activity == "Livestock", "0", "1")))

Hunting_test <- subset(Comparison_L_H, Catagory_Activity == "Hunting")

Livestock_test <- subset(Comparison_L_H, Catagory_Activity == "Livestock")

```

# Number of Threats

```{r}

boxplot(Comparison_L_H$Threats_TotalRelaventMentioned~Comparison_L_H$Catagory_Activity, ylab = "Number of relevent threats")

plot(Comparison_L_H$Total_kg_y, Comparison_L_H$Threats_TotalRelaventMentioned)

hist(Comparison_L_H$Total_kg_y)
hist(Active_SFS$Total_kg_y)
hist(Active_SFS$Threats_TotalRelaventMentioned)
hist(Comparison_L_H$Threats_TotalRelaventMentioned)

```

# Number of Threats Comparison

```{r}

#Livestock vs Hunting
Comparison.m1 <- glm(Comparison_L_H$Threats_TotalRelaventMentioned~Comparison_L_H$Catagory_Activity)
summary(Comparison.m1)

Comparison.Poison <- glm(Comparison_L_H$Threats_TotalRelaventMentioned~Comparison_L_H$Catagory_Activity, family = poisson)
summary(Comparison.Poison)

Comparison.Q <- glm(Comparison_L_H$Threats_TotalRelaventMentioned~Comparison_L_H$Catagory_Activity, family = quasipoisson)
summary(Comparison.Q)

par(mfrow=c(2,2))
plot(Comparison.m1)

#Prov Rate

ComparisonProvR <- glm(Comparison_L_H$Threats_TotalRelaventMentioned~Comparison_L_H$Total_kg_y, family = quasipoisson)
summary(ComparisonProvR)

```


#Comparison of each seperate threat

```{r Powerlines}

#Powerlines

T_Powerlines_glm2 <- glm(Threats_Powerlines~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(T_Powerlines_glm2)
T_Powerlines_fit2 <-simulateResiduals(T_Powerlines_glm2, n=250, refit = F)
plot(T_Powerlines_fit2)
confint(T_Powerlines_glm2)
confint.glm(T_Powerlines_glm2)
T_Powerlines_glm2$coefficients[2]+qt(0.025, 69)*0.5441  ; T_Powerlines_glm2$coefficients[2]+qt(0.975, 69)*0.5441
emmeans(T_Powerlines_glm2)

T_Powerlines_glm2_emmeans <- emmeans(T_Powerlines_glm2, ~ Catagory_Activity)
T_Powerlines_glm2_emmeans
summary(T_Powerlines_glm2_emmeans, type = "response")

table(Livestock_test$Threats_Powerlines) # No 18 ; Yes 34
table(Hunting_test$Threats_Powerlines)   # No 9 ; Yes 10

```

```{r Belief-based use}

#Belief-based use

T_BeliefB_glm2 <- glm(Threats_Muthi ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(T_BeliefB_glm2)
T_BeliefB_fit2 <-simulateResiduals(T_BeliefB_glm2, n=250, refit = F)
plot(T_BeliefB_fit2)
confint(T_BeliefB_glm2)
emmeans(T_BeliefB_glm2)

T_BeliefB_glm2_emmeans <- emmeans(T_BeliefB_glm2, ~ Catagory_Activity)
T_BeliefB_glm2_emmeans
summary(T_BeliefB_glm2_emmeans, type = "response")


table(Livestock_test$Threats_Muthi) # No 26 ; Yes 26
table(Hunting_test$Threats_Muthi)   # No 12 ; Yes 7

```

```{r Unintentional poisoning}

#Unintentional poisoning

T_UnintPoisoning_glm2 <- glm(Threats_SUMPoisonUnintentional ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(T_UnintPoisoning_glm2)
T_UnintPoisoning_fit2 <-simulateResiduals(T_UnintPoisoning_glm2, n=250, refit = F)
plot(T_UnintPoisoning_fit2)
confint(T_UnintPoisoning_glm2)

T_UnintPoisoning_glm2_emmeans <- emmeans(T_UnintPoisoning_glm2, ~ Catagory_Activity)
T_UnintPoisoning_glm2_emmeans
summary(T_UnintPoisoning_glm2_emmeans, type = "response")

table(Livestock_test$Threats_SUMPoisonUnintentional) # No 26 ; Yes 26
table(Hunting_test$Threats_SUMPoisonUnintentional)   # No 13 ; Yes 6

```

```{r Intentional poisoning}

#Intentional poisoning

T_IntPoisoning_glm2 <- glm(Threats_SUMPoisonIntentional~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(T_IntPoisoning_glm2)
T_IntPoisoning_fit2 <-simulateResiduals(T_IntPoisoning_glm2, n=250, refit = F)
plot(T_IntPoisoning_fit2)
confint(T_IntPoisoning_glm2)

T_IntPoisoning_glm2_emmeans <- emmeans(T_IntPoisoning_glm2, ~ Catagory_Activity)
T_IntPoisoning_glm2_emmeans
summary(T_IntPoisoning_glm2_emmeans, type = "response")

table(Livestock_test$Threats_SUMPoisonIntentional) # No 40 ; Yes 12
table(Hunting_test$Threats_SUMPoisonIntentional)   # No 17 ; Yes 2

```

```{r Verterinary drugs}

#Verterinary drugs

T_VetD_glm2 <- glm(Threats_VeterinaryDrugs~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(T_VetD_glm2)
T_VetD_fit2 <-simulateResiduals(T_VetD_glm2, n=250, refit = F)
plot(T_VetD_fit2)
confint(T_VetD_glm2)

T_VetD_glm2_emmeans <- emmeans(T_VetD_glm2, ~ Catagory_Activity)
T_VetD_glm2_emmeans
summary(T_VetD_glm2_emmeans, type = "response")

table(Livestock_test$Threats_VeterinaryDrugs) # No 40 ; Yes 12
table(Hunting_test$Threats_VeterinaryDrugs)   # No 17 ; Yes 2

```

```{r Habitat loss/ degredation}

#Habitat loss/ degredation

T_HabitatLoss_glm2 <- glm(Threats_HabitatLossDegredation ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(T_HabitatLoss_glm2)
T_HabitatLoss_fit2 <-simulateResiduals(T_HabitatLoss_glm2, n=250, refit = F)
plot(T_HabitatLoss_fit2)
T_HabitatLoss_glm2_fit <- emmeans(T_HabitatLoss_glm2, ~ Catagory_Activity)
T_HabitatLoss_glm2_fit_sum <- summary(T_HabitatLoss_glm2_fit, type = "response")
print(T_HabitatLoss_glm2_fit_sum)

plogis(confint(T_HabitatLoss_glm2)) #transform from log scale to probability scale?

T_HabitatLoss_glm2_emmeans <- emmeans(T_HabitatLoss_glm2, ~ Catagory_Activity)
T_HabitatLoss_glm2_emmeans
summary(T_HabitatLoss_glm2_emmeans, type = "response")


table(Livestock_test$Threats_HabitatLossDegredation) # No 47 ; Yes 5
table(Hunting_test$Threats_HabitatLossDegredation)   # No 14 ; Yes 5

```

```{r Food availibility}

#Food availibility

T_FoodAvail_glm2 <- glm(Threats_FoodAvailability ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(T_FoodAvail_glm2)
T_FoodAvail_fit2 <-simulateResiduals(T_FoodAvail_glm2, n=250, refit = F)
plot(T_FoodAvail_fit2)
confint(T_FoodAvail_glm2)

T_FoodAvail_glm2_emmeans <- emmeans(T_FoodAvail_glm2, ~ Catagory_Activity)
T_FoodAvail_glm2_emmeans
summary(T_FoodAvail_glm2_emmeans, type = "response")


table(Livestock_test$Threats_FoodAvailability) # No 44 ; Yes 8
table(Hunting_test$Threats_FoodAvailability)   # No 19 ; Yes 0

```

```{r Lead Poisoning}

#Lead Poisoning

T_LeadP_glm2 <- glm(Threats_LeadPoisoning ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(T_LeadP_glm2)
T_LeadP_fit2 <-simulateResiduals(T_LeadP_glm2, n=250, refit = F)
plot(T_LeadP_fit2)
confint(T_LeadP_glm2)

T_LeadP_glm2_emmeans <- emmeans(T_LeadP_glm2, ~ Catagory_Activity)
T_LeadP_glm2_emmeans
summary(T_LeadP_glm2_emmeans, type = "response")

table(Livestock_test$Threats_LeadPoisoning) # No 50 ; Yes 2
table(Hunting_test$Threats_LeadPoisoning)   # No 18 ; Yes 1

```

```{r Wind turbines}

# Wind turbines

T_WindT_glm2 <- glm(Threats_WindTurbines ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(T_WindT_glm2)
T_WindT_fit2 <-simulateResiduals(T_WindT_glm2, n=250, refit = F)
plot(T_WindT_fit2)
confint(T_WindT_glm2)

T_WindT_glm2_emmeans <- emmeans(T_WindT_glm2, ~ Catagory_Activity)
T_WindT_glm2_emmeans
summary(T_WindT_glm2_emmeans, type = "response")

table(Livestock_test$Threats_WindTurbines) # No 48 ; Yes 4
table(Hunting_test$Threats_WindTurbines)   # No 19 ; Yes 0

```

```{r human disturbance}

# human disturbance

T_HumanDist_glm2 <- glm(Threats_HumanDisturbance ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(T_HumanDist_glm2)
T_HumanDist_fit2 <-simulateResiduals(T_HumanDist_glm2, n=250, refit = F)
plot(T_HumanDist_fit2)
confint(T_HumanDist_glm2)

T_HumanDist_glm2_emmeans <- emmeans(T_HumanDist_glm2, ~ Catagory_Activity)
T_HumanDist_glm2_emmeans
summary(T_HumanDist_glm2_emmeans, type = "response")

table(Livestock_test$Threats_HumanDisturbance) # No 50 ; Yes 2
table(Hunting_test$Threats_HumanDisturbance)   # No 19 ; Yes 0

```

```{r vulture persercution}

# vulture persercution

T_VPersecution_glm2 <- glm(Threats_VulturePersecution ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(T_VPersecution_glm2)
T_VPersecution_fit2 <-simulateResiduals(T_VPersecution_glm2, n=250, refit = F)
plot(T_VPersecution_fit2)
confint(T_VPersecution_glm2)

T_VPersecution_glm2_emmeans <- emmeans(T_VPersecution_glm2, ~ Catagory_Activity)
T_VPersecution_glm2_emmeans
summary(T_VPersecution_glm2_emmeans, type = "response")

table(Livestock_test$Threats_VulturePersecution) # No 51 ; Yes 1
table(Hunting_test$Threats_VulturePersecution)   # No 18 ; Yes 1

```

```{r drowning}

#drowning

T_Drowning_glm2 <- glm(Threats_Drowning ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(T_Drowning_glm2)
T_Drowning_fit2 <-simulateResiduals(T_Drowning_glm2, n=250, refit = F)
plot(T_Drowning_fit2)
confint(T_Drowning_glm2)

T_Drowning_glm2_emmeans <- emmeans(T_Drowning_glm2, ~ Catagory_Activity)
T_Drowning_glm2_emmeans
summary(T_Drowning_glm2_emmeans, type = "response")

table(Livestock_test$Threats_Drowning) # No 51 ; Yes 1
table(Hunting_test$Threats_Drowning)   # No 19 ; Yes 0

```

```{r vehicle collisions}

#vehicle collisions

T_VehicleCol_glm2 <- glm(Threats_SUMVehicleCollisions ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(T_VehicleCol_glm2)
T_VehicleCol_fit2 <-simulateResiduals(T_VehicleCol_glm2, n=250, refit = F)
plot(T_VehicleCol_fit2)
confint(T_VehicleCol_glm2)

T_VehicleCol_glm2_emmeans <- emmeans(T_VehicleCol_glm2, ~ Catagory_Activity)
T_VehicleCol_glm2_emmeans
summary(T_VehicleCol_glm2_emmeans, type = "response")

table(Livestock_test$Threats_SUMVehicleCollisions) # No 52 ; Yes 0
table(Hunting_test$Threats_SUMVehicleCollisions)   # No 17 ; Yes 2

```

```{r nest site loss}

#nest site loss

T_NestSiteLoss_glm2 <- glm(Threats_NestSiteLoss ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(T_NestSiteLoss_glm2)
T_NestSiteLoss_fit2 <-simulateResiduals(T_NestSiteLoss_glm2, n=250, refit = F)
plot(T_NestSiteLoss_fit2)
confint(T_NestSiteLoss_glm2)

T_NestSiteLoss_glm2_emmeans <- emmeans(T_NestSiteLoss_glm2, ~ Catagory_Activity)
T_NestSiteLoss_glm2_emmeans
summary(T_NestSiteLoss_glm2_emmeans, type = "response")

table(Livestock_test$Threats_NestSiteLoss) # No 51 ; Yes 1
table(Hunting_test$Threats_NestSiteLoss)   # No 18 ; Yes 1

```

```{r Disease}

#Disease

T_Disease_glm2 <- glm(Threats_Disease ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(T_Disease_glm2)
T_Disease_fit2 <-simulateResiduals(T_Disease_glm2, n=250, refit = F)
plot(T_Disease_fit2)
confint(T_Disease_glm2)

T_Disease_glm2_emmeans <- emmeans(T_Disease_glm2, ~ Catagory_Activity)
T_Disease_glm2_emmeans
summary(T_Disease_glm2_emmeans, type = "response")

table(Livestock_test$Threats_Disease) # No 51 ; Yes 1
table(Hunting_test$Threats_Disease)   # No 19 ; Yes 0

```

```{r climate change}

#climate change

T_ClimChan_glm2 <- glm(Threats_ClimateChange ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(T_ClimChan_glm2)
T_ClimChan_fit2 <-simulateResiduals(T_ClimChan_glm2, n=250, refit = F)
plot(T_ClimChan_fit2)
confint(T_ClimChan_glm2)

T_ClimChan_glm2_emmeans <- emmeans(T_ClimChan_glm2, ~ Catagory_Activity)
T_ClimChan_glm2_emmeans
summary(T_ClimChan_glm2_emmeans, type = "response")

table(Livestock_test$Threats_ClimateChange) # No 52 ; Yes 0
table(Hunting_test$Threats_ClimateChange)   # No 19 ; Yes 0

```


# Benefits

```{r Cleaning Service}

#Cleaning Service

B_CleaningServ_glm2 <- glm(Benefits_CleaningServiceSUM ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(B_CleaningServ_glm2)
B_CleaningServ_fit2 <-simulateResiduals(B_CleaningServ_glm2, n=250, refit = F)
plot(B_CleaningServ_fit2)
confint(B_CleaningServ_glm2)

B_CleaningServ_glm2_emmeans <- emmeans(B_CleaningServ_glm2, ~ Catagory_Activity)
B_CleaningServ_glm2_emmeans
summary(B_CleaningServ_glm2_emmeans, type = "response")

table(Livestock_test$Benefits_CleaningServiceSUM) # No 21 ; Yes 31
table(Hunting_test$Benefits_CleaningServiceSUM)   # No 12 ; Yes 7

```

```{r Personal Enjoyment}

#Personal Enjoyment

B_PEnjoy_glm2 <- glm(Benefits_PersonalSatisfactionEnjoySUM ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(B_PEnjoy_glm2)
B_PEnjoy_glm_fit2 <-simulateResiduals(B_PEnjoy_glm2, n=250, refit = F)
plot(B_PEnjoy_glm_fit2)
confint(B_PEnjoy_glm2)

B_PEnjoy_glm2_emmeans <- emmeans(B_PEnjoy_glm2, ~ Catagory_Activity)
B_PEnjoy_glm2_emmeans
summary(B_PEnjoy_glm2_emmeans, type = "response")

table(Livestock_test$Benefits_PersonalSatisfactionEnjoySUM) # No 35 ; Yes 17
table(Hunting_test$Benefits_PersonalSatisfactionEnjoySUM)   # No 14 ; Yes 5

```

```{r Conservation}

#Conservation

B_Conservation_glm2 <- glm(Benefits_ConservationSUM ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(B_Conservation_glm2)
B_Conservation_glm_fit2 <-simulateResiduals(B_Conservation_glm2, n=250, refit = F)
plot(B_Conservation_glm_fit2)
confint(B_Conservation_glm2)
x <- emmeans(B_Conservation_glm2, ~ Catagory_Activity)
summary(x, type = "response")
print(B_Ecotourism_glm2_fit_sum)

B_Conservation_glm2_emmeans <- emmeans(B_Conservation_glm2, ~ Catagory_Activity)
B_Conservation_glm2_emmeans
summary(B_Conservation_glm2_emmeans, type = "response")

table(Livestock_test$Benefits_ConservationSUM) # No 42 ; Yes 10
table(Hunting_test$Benefits_ConservationSUM)   # No 17 ; Yes 2

```

```{r Ecotourism}
#Ecotourism

B_Ecotourism_glm2 <- glm(Benefits_Ecotourism ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(B_Ecotourism_glm2)
confint(B_Ecotourism_glm2)
B_Ecotourism_fit2 <-simulateResiduals(B_Ecotourism_glm2, n=250, refit = F)
plot(B_Ecotourism_fit2)
B_Ecotourism_glm2_fit <- emmeans(B_Ecotourism_glm2, ~ Catagory_Activity)
B_Ecotourism_glm2_fit_sum <- summary(B_Ecotourism_glm2_fit, type = "response")
print(B_Ecotourism_glm2_fit_sum)
plot(B_Ecotourism_glm2_fit_sum)
# Catagory_Activity   prob     SE  df asymp.LCL asymp.UCL
 #Hunting           0.2632 0.1010 Inf   0.11398     0.498
# Livestock         0.0385 0.0267 Inf   0.00964     0.141
# thus hunters are  0.2632 / 0.0385 times more likely to mention ecotourism (or 0.2632-0.0385% more likely)

Ecotourism_plot <- ggplot(B_Ecotourism_glm2_fit_sum, aes(x = Catagory_Activity, y=prob)) +
  geom_bar(stat="identity", width = 0.4, fill = "Grey") +
  geom_errorbar(aes(ymin=asymp.LCL, ymax=asymp.UCL), width=0.06,position=position_dodge(.9)) +
  labs(x = "", y = "Probability of mentioning ecotourism \n ") +
  scale_x_discrete(labels=c("Hunting", "Livestock \n farming")) +
  theme_classic() +
  theme(aspect.ratio = 2/1)

B_Ecotourism_glm2_emmeans <- emmeans(B_Ecotourism_glm2, ~ Catagory_Activity)
B_Ecotourism_glm2_emmeans
summary(B_Ecotourism_glm2_emmeans, type = "response")

table(Livestock_test$Benefits_Ecotourism) # No 50 ; Yes 2
table(Hunting_test$Benefits_Ecotourism)   # No 14 ; Yes 5

```

```{r BNone}
#None

B_None_glm2 <- glm(Benefits_None ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(B_None_glm2)
B_None_fit2 <-simulateResiduals(B_None_glm2, n=250, refit = F)
plot(B_None_fit2)
confint(B_None_glm2)

B_None_glm2_emmeans <- emmeans(B_None_glm2, ~ Catagory_Activity)
B_None_glm2_emmeans
summary(B_None_glm2_emmeans, type = "response")

table(Livestock_test$Benefits_None) # No 46 ; Yes 6
table(Hunting_test$Benefits_None)   # No 14 ; Yes 5

```

```{r Research}

#Research

B_Research_glm2 <- glm(Benefits_Research ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(B_Research_glm2)
confint(B_Research_glm2)
B_Research_fit2 <-simulateResiduals(B_Research_glm2, n=250, refit = F)
plot(B_Research_fit2)

B_Research_glm2_emmeans <- emmeans(B_Research_glm2, ~ Catagory_Activity)
B_Research_glm2_emmeans
summary(B_Research_glm2_emmeans, type = "response")

table(Livestock_test$Benefits_Research) # No 51 ; Yes 1
table(Hunting_test$Benefits_Research)   # No 18 ; Yes 1

```

```{r Locating Mortalities}

#Locating Mortalities

B_LocatingMortalities_glm2 <- glm(Benefits_FindingAnimals ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(B_LocatingMortalities_glm2)
B_LocatingMortalities_fit2 <-simulateResiduals(B_LocatingMortalities_glm2, n=250, refit = F)
plot(B_LocatingMortalities_fit2)
confint(B_LocatingMortalities_glm2)
B_LocatingMortalities_glm2_emmeans <- emmeans(B_LocatingMortalities_glm2, ~ Catagory_Activity)
B_LocatingMortalities_glm2_emmeans
summary(B_LocatingMortalities_glm2_emmeans, type = "response")

B_LocatingMortalities_glm2_emmeans <- emmeans(B_LocatingMortalities_glm2, ~ Catagory_Activity)
B_LocatingMortalities_glm2_emmeans
summary(B_LocatingMortalities_glm2_emmeans, type = "response")

library(rcompanion)

groupwiseMean(Benefits_FindingAnimals ~ 1,
              data   = Hunting_test,
              conf   = 0.95,
              digits = 3)

D_ProbAnimal_glm2$coefficients[2]+qt(0.025, 69)*2141.7604  ; D_ProbAnimal_glm2$coefficients[2]+qt(0.975, 69)*2141.7604

table(Livestock_test$Benefits_FindingAnimals) # No 52 ; Yes 0
table(Hunting_test$Benefits_FindingAnimals)   # No 18 ; Yes 1

```

```{r Disease prevention }

#Disease prevention 

B_DiseasePrevention_glm2 <- glm(Benefits_DiseaseManagement ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(B_DiseasePrevention_glm2)
B_DiseasePrevention_fit2 <-simulateResiduals(B_DiseasePrevention_glm2, n=250, refit = F)
plot(B_DiseasePrevention_fit2)
confint(B_DiseasePrevention_glm2)

B_DiseasePrevention_glm2_emmeans <- emmeans(B_DiseasePrevention_glm2, ~ Catagory_Activity)
B_DiseasePrevention_glm2_emmeans
summary(B_DiseasePrevention_glm2_emmeans, type = "response")

table(Livestock_test$Benefits_DiseaseManagement) # No 51 ; Yes 1
table(Hunting_test$Benefits_DiseaseManagement)   # No 19 ; Yes 0

```


# Disadvantagous

```{r DNone}

#None

D_None_glm2 <- glm(Disadvantageous_Nothing ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(D_None_glm2)
confint(D_None_glm2)
D_None_fit2 <-simulateResiduals(D_None_glm2, n=250, refit = F)
plot(D_None_fit2)
D_None_glm2_fit <- emmeans(D_None_glm2, ~ Catagory_Activity)
D_None_glm2_fit_sum <- summary(D_None_glm2_fit, type = "response")
print(D_None_glm2_fit_sum)

#Catagory_Activity  prob     SE  df asymp.LCL asymp.UCL
 #Hunting           0.789 0.0935 Inf     0.554     0.919
 #Livestock         0.500 0.0693 Inf     0.367     0.633

#Hunters are thus 0.789/0.500 times more likely to perceive no disadvantage (or 0.789-0.500% more likely)

None <- ggplot(D_None_glm2_fit_sum, aes(x = Catagory_Activity, y=prob)) +
  geom_bar(stat="identity", width = 0.4, fill = "Grey") +
  geom_errorbar(aes(ymin=asymp.LCL, ymax=asymp.UCL), width=0.06,position=position_dodge(.9)) +
  labs(x = "", y = "Probability of specifying no disadvantages \n ") +
  scale_x_discrete(labels=c("Hunting", "Livestock \n farming")) +
  theme_classic() +
  theme(aspect.ratio = 2/1)

D_None_glm2_emmeans <- emmeans(D_None_glm2, ~ Catagory_Activity)
D_None_glm2_emmeans
summary(D_None_glm2_emmeans, type = "response")

table(Livestock_test$Disadvantageous_Nothing) # No 26 ; Yes 26
table(Hunting_test$Disadvantageous_Nothing)   # No 4  ; Yes 15

```

```{r}

# Maintenance

D_CleaningServ_glm2 <- glm(Disadvantageous_CleaningMaintananceSUM ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(D_CleaningServ_glm2)
confint(D_CleaningServ_glm2)
D_CleaningServ_fit2 <-simulateResiduals(D_CleaningServ_glm2, n=250, refit = F)
plot(D_CleaningServ_fit2)

D_CleaningServ_glm2_emmeans <- emmeans(D_CleaningServ_glm2, ~ Catagory_Activity)
D_CleaningServ_glm2_emmeans
summary(D_CleaningServ_glm2_emmeans, type = "response")

table(Livestock_test$Disadvantageous_CleaningMaintananceSUM) # No 46 ; Yes 6
table(Hunting_test$Disadvantageous_CleaningMaintananceSUM)   # No 18 ; Yes 1

```

```{r}
#Problem animals

D_ProbAnimal_glm2 <- glm(Disadvantageous_ProblemAnimalsIncreaseSUM ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(D_ProbAnimal_glm2)
D_ProbAnimal_fit2 <-simulateResiduals(D_ProbAnimal_glm2, n=250, refit = F)
plot(D_ProbAnimal_fit2)
confint(D_ProbAnimal_glm2) #get compeltely different answers
D_ProbAnimal_glm2$coefficients[2]+qt(0.025, 69)*2141.7604  ; D_ProbAnimal_glm2$coefficients[2]+qt(0.975, 69)*2141.7604

D_ProbAnimal_glm2_emmeans <- emmeans(D_ProbAnimal_glm2, ~ Catagory_Activity)
D_ProbAnimal_glm2_emmeans
summary(D_ProbAnimal_glm2_emmeans, type = "response")

table(Livestock_test$Disadvantageous_ProblemAnimalsIncreaseSUM) # No 42 ; Yes 10
table(Hunting_test$Disadvantageous_ProblemAnimalsIncreaseSUM)   # No 19 ; Yes 0

```

```{r}
#Site security

D_SSecurity_glm2 <- glm(Disadvantageous_SiteSecuritySUM ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(D_SSecurity_glm2)
D_SSecurity_fit2 <-simulateResiduals(D_SSecurity_glm2, n=250, refit = F)
plot(D_SSecurity_fit2)
confint(D_SSecurity_glm2)
D_SSecurity_glm2$coefficients[2]+qt(0.025, 69)*1.1299  ; D_SSecurity_glm2$coefficients[2]+qt(0.975, 69)*1.1299 # Differs slightly from above

D_SSecurity_glm2_emmeans <- emmeans(D_SSecurity_glm2, ~ Catagory_Activity)
D_SSecurity_glm2_emmeans
summary(D_SSecurity_glm2_emmeans, type = "response")

table(Livestock_test$Disadvantageous_SiteSecuritySUM) # No 47 ; Yes 5
table(Hunting_test$Disadvantageous_SiteSecuritySUM)   # No 18 ; Yes 1

```

```{r}

#Untidy

D_Untidy_glm2 <- glm(Disadvantageous_UnsightlyUncleanUntidy ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(D_Untidy_glm2)
D_Untidy_fit2 <-simulateResiduals(D_Untidy_glm2, n=250, refit = F)
plot(D_Untidy_fit2)
confint(D_Untidy_glm2)
D_Untidy_glm2$coefficients[2]+qt(0.025, 69)*0.7855  ; D_Untidy_glm2$coefficients[2]+qt(0.975, 69)*0.7855 #differs slightly from above

D_Untidy_glm2_emmeans <- emmeans(D_Untidy_glm2, ~ Catagory_Activity)
D_Untidy_glm2_emmeans
summary(D_Untidy_glm2_emmeans, type = "response")

table(Livestock_test$Disadvantageous_UnsightlyUncleanUntidy) # No 47 ; Yes 5
table(Hunting_test$Disadvantageous_UnsightlyUncleanUntidy)   # No 16 ; Yes 3

```

```{r}

#Smell

D_Smell_glm2 <- glm(Disadvantageous_Smell ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(D_Smell_glm2)
D_Smell_fit2 <-simulateResiduals(D_Smell_glm2, n=250, refit = F)
plot(D_Smell_fit2)
confint(D_Smell_glm2)
D_Smell_glm2$coefficients[2]+qt(0.025, 69)*1.18710  ; D_Smell_glm2$coefficients[2]+qt(0.975, 69)*1.18710 #differs from above

D_Smell_glm2_emmeans <- emmeans(D_Smell_glm2, ~ Catagory_Activity)
D_Smell_glm2_emmeans
summary(D_Smell_glm2_emmeans, type = "response")

table(Livestock_test$Disadvantageous_Smell) # No 49 ; Yes 3
table(Hunting_test$Disadvantageous_Smell)   # No 18 ; Yes 1

```

```{r}

#Disease

D_Disease_glm2 <- glm(Disadvantageous_Disease ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(D_Disease_glm2)
D_Disease_fit2 <-simulateResiduals(D_Disease_glm2, n=250, refit = F)
plot(D_Disease_fit2)
confint(D_Disease_glm2)
D_Disease_glm2$coefficients[2]+qt(0.025, 69)*1.1299  ; D_Disease_glm2$coefficients[2]+qt(0.975, 69)*1.1299 #differs slightly form above

D_Disease_glm2_emmeans <- emmeans(D_Disease_glm2, ~ Catagory_Activity)
D_Disease_glm2_emmeans
summary(D_Disease_glm2_emmeans, type = "response")

table(Livestock_test$Disadvantageous_Disease) # No 47 ; Yes 5
table(Hunting_test$Disadvantageous_Disease)   # No 18 ; Yes 1

```

```{r}

#Carcass sourcing

D_CarcassSourcing_glm2 <- glm(Disadvantageous_CarcassSourcing ~ Catagory_Activity, family = binomial, data = Comparison_L_H)
summary(D_CarcassSourcing_glm2)
D_CarcassSourcing_fit2 <-simulateResiduals(D_CarcassSourcing_glm2, n=250, refit = F)
plot(D_CarcassSourcing_fit2)
confint(D_CarcassSourcing_glm2)
D_CarcassSourcing_glm2$coefficients[2]+qt(0.025, 69)*4067.6259 ; D_CarcassSourcing_glm2$coefficients[2]+qt(0.975, 69)*4067.6259

D_CarcassSourcing_glm2_emmeans <- emmeans(D_CarcassSourcing_glm2, ~ Catagory_Activity)
D_CarcassSourcing_glm2_emmeans
summary(D_CarcassSourcing_glm2_emmeans, type = "response")

table(Livestock_test$Disadvantageous_CarcassSourcing) # No 50 ; Yes 2
table(Hunting_test$Disadvantageous_CarcassSourcing)   # No 19 ; Yes 0

```


